Resurgence of the Airy function

### 2022-03-29 airy-resurgence.tex
Correct notation for asymptotics of v_1 and v_{-1}

In Sections \ref{pos-root}\,--\,\ref{neg-root}, we'll see this approach succeed. For each root $\alpha$, we'll find a solution $v_\alpha$ of equation~\ref{diff-eq:spatial-mod-bessel} which is slight and locally integrable at $\zeta = \alpha$. Calling its order $\tau_\alpha$, we'll normalize it so that $v_\alpha \sim \zeta^{\tau_\alpha}$ at $\zeta = \alpha$. We know $\laplace_{\zeta, \alpha} v_\alpha$ will satisfy equation~\ref{eqn:reg-mod-bessel}, and we can even work out its asymptotics. We know from Section~\ref{translation} that

@@

where $V_\alpha = \laplace_{\zeta_\alpha, 0} v_\alpha$ and $\zeta = \alpha + \zeta_\alpha$, and we know from Section~\ref{reg-decay} that $V_\alpha \sim \Gamma(1 + \tau_\alpha)\,z^{-1 - \tau_\alpha}$ at $z = \infty$. Now we can write our solution as

@@

where $W_\alpha = z^{\tau_\alpha} V_\alpha$ is asymptotic to $\Gamma(1 + \tau_\alpha)\,z^{-1}$ at $z = \infty$.

@@

From the argument in Section~\ref{big-idea}, we know that $\laplace_{\zeta, 1} v_1$ satisfies equation~\ref{eqn:mod-bessel}, and can be written as $e^{-z} V_1$, where $V_1 = \laplace_{\zeta_1, 0} v_1$. Observing that $v_1$ has order $-1/2$, we learn that $V_1 = z^{1/2} W_1$ with $W_1 \sim \Gamma\big(\tfrac{1}{2}\big)\,z^{-1}$ at $z = \infty$.

@@

where $\zeta_{-1}$ is the coordinate with $\zeta = -1 + \zeta_{-1}$. From the argument in Section~\ref{big-idea}, we know that $\laplace_{\zeta, -1} v_{-1}$ satisfies equation~\ref{eqn:mod-bessel}, and can be written as $e^z V_{-1}$, where $V_{-1} = \laplace_{\zeta_{-1}, 0} v_{-1}$. Like our other solution, $v_{-1}$ has order $-1/2$, we again have $V_{-1} = z^{1/2} W_{-1}$ for some $W_{-1} \in o_{z \to \infty}(z^{-1})$.

>>>>

In Sections \ref{pos-root}\,--\,\ref{neg-root}, we'll see this approach succeed. For each root $\alpha$, we'll find a solution $v_\alpha$ of equation~\ref{diff-eq:spatial-mod-bessel} which is slight and locally integrable at $\zeta = \alpha$. We know the function $\laplace_{\zeta, \alpha} v_\alpha$ will satisfy equation~\ref{eqn:reg-mod-bessel}, and we can even find its asymptotics from the order $\tau_\alpha$ of $v_\alpha$. We learned in Section~\ref{translation} that

@@

where $V_\alpha = \laplace_{\zeta_\alpha, 0} v_\alpha$ and $\zeta = \alpha + \zeta_\alpha$, and we learned in Section~\ref{reg-decay} that $V_\alpha$ is asymptotic to a scalar multiple of $z^{-1 - \tau_\alpha}$ at $z = \infty$. That means we can write our solution as

@@

where $W_\alpha = z^{\tau_\alpha} V_\alpha$ is asymptotic to a scalar multiple of $z^{-1}$ at $z = \infty$.

@@

From the argument in Section~\ref{big-idea}, we know that $\laplace_{\zeta, 1} v_1$ satisfies equation~\ref{eqn:mod-bessel}, and can be written as $e^{-z} V_1$, where $V_1 = \laplace_{\zeta_1, 0} v_1$. Observing that $v_1$ has order $-1/2$, we learn that $V_1 = z^{1/2} W_1$ for some $W_1$ which is asymptotic to a scalar multiple of $z^{-1}$ at $z = \infty$.

@@

where $\zeta_{-1}$ is the coordinate with $\zeta = -1 + \zeta_{-1}$. From the argument in Section~\ref{big-idea}, we know that $\laplace_{\zeta, -1} v_{-1}$ satisfies equation~\ref{eqn:mod-bessel}, and can be written as $e^z V_{-1}$, where $V_{-1} = \laplace_{\zeta_{-1}, 0} v_{-1}$. Like our other solution, $v_{-1}$ has order $-1/2$, we again have $V_{-1} = z^{1/2} W_{-1}$ for some $W_1$ which is asymptotic to a scalar multiple of $z^{-1}$ at $z = \infty$.
